---
output:
  html_document: default
  pdf_document: default
---
# The Supply and Demand Model

## Section X

This is my introduction.

```{r chunk-x}
x <- 1
print(x)
```


### Subsection 1

Here are some details.

### Subsection 2

These are more details.

## Section Y

This is another section.

```{r chunk-y}
y <- 2
print(y)
```



This unit focuses on the Supply and Demand model, a theoretical tool that shows how prices are shaped by the market interaction of sellers and buyers.  

Its malleability and simplicity makes this the most widely used model in economics.

You can use the model to analyze a wide variety of markets: markets for consumer goods and services, financial markets,  healthcare and insurance markets, labor markets among others.

LEARNING OBJECTIVES.  By the end of this unit you will be able to:

\begin{equation}
\sum_{k=1}^{n} \frac{1}{2^k}
\end{equation}

\begin{tabular}{|l|r|r|} \hline
Item & Qty & Unit \$ \\\hline
Widget & 1 & 10 \\
Gadget & 2 & 11 \\\hline
\end{tabular}


\[
4x^3 + 43
\]


1. Formulate conjectures on the source of price variations and identify data you could use to test these conjectures.
1. Use mathematical formalizations (equations and graphs) to represent the Supply and Demand model and to analyze and evaluate how economic shocks affect prices. 
1. Use the Supply and Demand model to analyze the outcomes of various public policies.
1. Clearly explain your economic reasoning demonstrating fluency in Supply and Demand terminology. 



