---
title: "Pre-class activity week 2 micro"
author: "Noah Love: NL2658"
date: "9/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sue's budget

Read the following narrative and in a graph measuring carrots along the horizontal axis and soda along the vertical axis draw Sue's budget set. What is the expression of Sue's budget constraint?                
Sue has $10 to buy soda and carrots. Soda costs $1 per bottle. Carrots cost $1 per pack for the first four packs and $2 per pack afterwards.

##### Solution

We can start by making a table of values if we want:

| Soda | Carrots |
|------|---------|
| 10   | 0       |
| 9    | 1       |
| 8    | 2       |
| 7    | 3       |
| 6    | 4       |
| 4    | 5       |
| 2    | 6       |
| 0    | 7       |

From this, we can concluse that we need to describe the function piecewise, with the first line being from $x = 0$ to $x = 4$. When $x = 4$, the carrots cost more so the slop is greater. 

Therefore, from $x = 0$ to $x = 4$, the formula is $$10 - x$$ meaning that with 0 carrots ($x = 0$), Sue buys 10 sodas. She can trade off one soda for one carrot up until $x = 5$. At $x = 5$, carrots are now costing two sodas, or \$2 dollars each, meaning the rate (or slope) doubles for $-x$ to $-2x$. Together:

$$B_S = \begin{cases}
10 - x & \text{for } 0 \leq x \leq 4 \\
14 - 2x & \text{for } 4 \leq x \leq 7
\end{cases}$$

As a graph:

```{r}

func <- function(x){(0 <= x & x < 4)*(10-x)+(4 <= x & x < 7)*(14-2*x)}
vectFunc <- Vectorize(func)
plot(vectFunc,0,8, type = "l", col = "blue", ylab = "Soda", xlab = "Carrots", main = "Sue's Budget")
abline(v = 0, h = 0)

```



